### 2019-06-06 2-Chapters/1-Chapter/chapter1.tex
Added leftbar to all defn,cor,thm etc

\paragraph{Copyright notice.}
%
This document and the additional resources required to compile it (including \LaTeX{} code, Python snippets, images etc)
are \href{https://github.com/Naereen/phd-thesis/}{publicly published},
online at \href{https://github.com/Naereen/phd-thesis/}{\texttt{GitHub.com/Naereen/phd-thesis/}},
under the terms of the open-source \href{https://lbesson.mit-license.org/}{\emph{MIT License}}.

>>>>

\paragraph{Copyright notice.}
%
This document and the additional resources required to compile it (including \LaTeX{} code, Python snippets, images etc)
are \href{https://github.com/Naereen/phd-thesis/}{publicly published},
under the terms of the open-source \href{https://lbesson.mit-license.org/}{\emph{MIT License}},
online at \\
\href{https://github.com/Naereen/phd-thesis/}{\texttt{GitHub.com/Naereen/phd-thesis/}},

### 2019-06-06 2-Chapters/2-Chapter/IEEE_WCNC_2018.git/IEEE_WCNC__2018__Paper__Lilian_Besson__07-17.tex
Added leftbar to all defn,cor,thm etc

Our proposed \Aggr{} is detailed in Algorithm~\ref{algo:25:Aggr}.
%
\begin{small}
	\begin{figure}[h!]
		\centering
		\begin{framed}
		% Documentation at http://mirror.ctan.org/tex-archive/macros/latex/contrib/algorithm2e/doc/algorithm2e.pdf if needed
		% Or https://en.wikibooks.org/wiki/LaTeX/Algorithms#Typesetting_using_the_algorithm2e_package
		\begin{algorithm}[H]
			% XXX Input, data and output
			\KwIn{$N$ bandit algorithms, $\Alg_1, \dots, \Alg_N$, with $N \geq 2$}
			\KwIn{Number of arms, $K \geq 2$}
			\KwIn{Time horizon, $T \geq 1$, \textbf{not} used for the learning}
			\KwIn{A sequence of learning rates, $(\eta_t)_{t \geq 1}$}
			\KwData{Initial uniform distribution, $\pi^{0} = \cU([N])$}
			\KwResult{$\Alg_{\mathrm{aggr}}=\Aggr\left[\Alg_1, \dots, \Alg_N\right]$}
			% XXX Algorithm
			\For(\tcp*[f]{At every time step})
            {$t = 1, \dots, T$}{
				%
				% \tcp{First, run each algorithm $\Alg_a$}
				\For(\tcp*[f]{Can be parallel}){$a = 1, \dots, N$}{
					$\Alg_a$ updates its internal state (e.g., \UCB{} indexes)\;
					It chooses $A_a(t+1) \in [K]$.
				}
				%
				% \tcp{The more algorithms have chosen arm $j$, the more probable it is to be chosen.}
				Let $p^{t+1}_j := \sum\limits_{a = 1}^{N} \pi^{t}_a \times \mathbbm{1}(\{A_a(t+1) = j\}), \;\forall 1\leq j \leq K$\;
				% \tcp*{Sum trusts}
				Then $\Alg_{\mathrm{aggr}}$ chooses arm $A(t+1) \sim p^{t+1}$\;
				% $\P(A(t+1)_{\mathrm{aggr}} = j) = p^{t+1}_j$
				% \tcp*{Sample once}
				%
				Give \emph{original} reward $(A(t+1), 1 - \ell_{A(t+1)}(t+1))$ to \emph{each} $\Alg_a$ (maybe \emph{not} on its chosen arm)\;
				Compute an \emph{unbiased} estimate of the loss of the trusted algorithms,$$ \ell^{t+1} = \ell_{A(t+1)}(t+1) / p^{t+1}_{A(t+1)}\;. $$
				% \tcp{Use bandit feedback to update $\pi^{t}$}
				% \tcp{Finally, use the instantaneous bandit feedback (loss $\ell_{A(t+1),t}$) to update $\pi^{t}$}
				% \For(\tcp*[f]{Can be parallel}){$a = 1, \dots, N$}{
				\For{$a = 1, \dots, N$}{
					% \eIf{$\Alg_a$ was trusted, \ie, $A_a(t+1) = A(t+1)$}{
					\eIf{$\Alg_a$ was trusted, \ie, $A_a(t+1) = A(t+1)$}{
						$ \pi^{t+1}_{a} = \exp(\eta_t \ell^{t+1}) \times \pi^{t}_{a} $
						\tcp*{Trusted more}
						}{
						% $ \pi^{t+1}_{a} = \exp(- \eta_t \ell^{t+1}) \times \pi^{t}_{a} $
						$ \pi^{t+1}_{a} = \pi^{t}_{a} $
						\tcp*{Do not update the trust now}
					}
				}
				Renormalize the new weights $\pi^{t+1}$: $\pi^{t+1} := \pi^{t+1} / \sum_{a=1}^{N} \pi^{t+1}_{a}$.
				% \tcp*{Project it back to $\Delta_N$}
			}
			\caption{Our algorithm \Aggr{} aggregating $\Alg_1,\dots,\Alg_N$.}
			\label{algo:25:Aggr}
		\end{algorithm}
		\end{framed}
	\end{figure}
\end{small}

At every time step, after having observed a loss $\ell_{A(t+1)}(t+1)$ for its chosen action $A(t+1)$,
the algorithm updates the trust probabilities from $\pi^t$ to $\pi^{t+1}$ by
a multiplicative exponential factor (using the learning rate and the \emph{unbiased} loss).
%
Only the algorithms $\Alg_a$ who advised the last decision get their trust updated, in order to trust more the ``reliable'' algorithms.

The loss estimate is unbiased in the following sense. If one had access to the rewards $r_k(t+1)$ (or the losses $\ell_k(t+1)$) for all arms $k$, the loss incurred by algorithm $a$ at time $t+1$ would be $\widetilde{\ell_{a,t+1}} = \ell_{A_a(t+1)}(t+1)$. This quantity can only be observed for those algorithms for which $A_{a}^{t+1}=A(t+1)$. However, by dividing by the probability of observing this recommendation, one obtains an unbiased estimate of $\widetilde{\ell_{a,t}}$. More precisely, if we define the estimate by
\begin{equation}
	\widehat{\ell_{a,t+1}} = \frac{\ell_{A_a(t+1)}(t+1)}{p_{A_a(t+1)}^{t+1}} \mathbbm{1}(A_a(t+1) = A(t+1))
\end{equation}
satisfies $\mathbb{E}[\widehat{\ell_{a,t+1}} | \mathcal{H}_t] = \widetilde{\ell_{a,t+1}}$, for all $a$, where the expectation is taken conditionally to the history of observations up to round $t$, $\mathcal{H}_{t}$. Observe that $\widetilde{\ell_{a,t+1}}=\ell^{t+1}$ for all algorithms $a$ such that $A_a(t+1)=A(t+1)$, and $\widetilde{\ell_{a,t+1}}=0$ otherwise.

% - Precise some tricky points
An important feature of \Aggr{} is the feedback provided to each underlying bandit algorithm, upon the observation of arm $A(t+1)$. Rather than updating only the trusted algorithms (that is the algorithms which would have drawn arm $A(t+1)$) with the observed reward $r_{A(t+1)}(t+1)=1 - \ell_{A(t+1)}(t+1)$,  we found that updating each algorithm with the (original) loss observed for arm $A(t+1)$ improves the performance drastically.
%
As expected, the more feedback they get, the faster the underlying algorithms learn, and the better the aggregation algorithm is.
This intuition is backed up by theory explained in \cite{Maillard11}.

@@

% ----------------------------------------------------------------------
\textbf{Comparison with \ExpQ{}:}\label{sub:25:Exp4}

% - explain, but don't give pseudo-code ?
The \ExpQ{} algorithm (see, e.g. \cite[Section 4.2]{Bubeck12})
is similar to \Aggr{}, presented in Algorithm \ref{algo:25:Aggr},
but differs in the two following points.
%
First, $a\sim\pi^t$ is sampled first and the arm chosen by $\Alg_a$ is trusted, whereas \Aggr{}
needs to listen to the $N$ decisions to perform the updates on $\pi^{t+1}$.
Then, \ExpQ{} gives back an observation (arm, reward) only to the last trusted algorithm
whereas \Aggr{} gives it to all algorithms.
%
Second, after having computed the loss estimate $\ell$, \ExpQ{} updates the estimated cumulative loss for each algorithm,
$\widetilde{L}_a(t) = \sum_{s=1}^{t} \ell_{A_a^s}(s) \times \mathbbm{1}(A^{s}_{a} = A^{s}_{\mathrm{aggr}})$.
%
Instead
\footnote{~It is the same for constant learning rates, and does not differ much for decreasing learning rates.}
of updating $\pi^{t}$ multiplicatively as we do for our proposal, \ExpQ{} recomputes it, proportionally to
$\exp(- \eta_t \widetilde{L}_a(t))$.

@@

Figures~\ref{fig:25:EasyBernoulli} and \ref{fig:25:HarderMixed} are in semilog-$y$ scale, this helps to see that the best algorithms can be an \emph{order of magnitude} more efficient than the worst, and the \Aggr{} performs similarly to the best ones, when the other aggregation algorithms are usually amongst the worst.
Figure~\ref{fig:25:HarderMixed_semilogx} is in semilog-$x$ scale to show that the regret of efficient algorithms are indeed logarithmic.

@@

For Bernoulli problems (Figures~\ref{fig:25:EasyBernoulli} and \ref{fig:25:HardBernoulli}), UCB with $\alpha=1/2$, Thompson sampling, BayesUCB and \klUCB{}$^+$ (with the binary $\kl$ function) all perform similarly, and \Aggr{} is found to be as efficient as all of them.
For Gaussian and exponential arms, rewards are truncated into $[0,1]$, and the variance of Gaussian distributions is fixed to $\sigma^2 = 0.05$ for all arms, and can be known to the algorithms (the \kl{} function is adapted to this one-dimensional exponential family).
%
Figure~\ref{fig:25:EasyGaussian} uses only Gaussian arms, with a large gap between their means and a relatively small variance, giving an ``easy'' problem.
%
And Figure~\ref{fig:25:HarderMixed} shows a considerably harder ``mixed'' problem, when the distributions are no longer in the same one-dimensional exponential family and so the Lai \& Robbins' lower-bound no longer holds (even if there still exists a lower-bound).

For each of the 4 problems considered, the \Aggr{} algorithm with default option (broadcast loss to all players) is the best of all the aggregation algorithms,
and its regret is very close to the best of the aggregated algorithms.
Especially in difficult problems with mixed or unknown distributions, \Aggr{} showed to be more efficient that \ExpQ{} and orders of magnitude better than the other reference aggregation algorithms \LearnExp{} and \CORRAL{} (see Figures~\ref{fig:25:HarderMixed} and \ref{fig:25:HarderMixed_semilogx}).

>>>>

Our proposed \Aggr{} is detailed in Algorithm~\ref{algo:25:Aggr}.
%
\begin{small}
	\begin{figure}[h!]
		\centering
		\begin{framed}
		% Documentation at http://mirror.ctan.org/tex-archive/macros/latex/contrib/algorithm2e/doc/algorithm2e.pdf if needed
		% Or https://en.wikibooks.org/wiki/LaTeX/Algorithms#Typesetting_using_the_algorithm2e_package
		\begin{algorithm}[H]
			% XXX Input, data and output
			\KwIn{$N$ bandit algorithms, $\Alg_1, \dots, \Alg_N$, with $N \geq 2$}
			\KwIn{Number of arms, $K \geq 2$}
			\KwIn{Time horizon, $T \geq 1$, \textbf{not} used for the learning}
			\KwIn{A sequence of learning rates, $(\eta_t)_{t \geq 1}$}
			\KwData{Initial uniform distribution, $\pi^{0} = \cU([N])$}
			\KwResult{$\Alg_{\mathrm{aggr}}=\Aggr\left[\Alg_1, \dots, \Alg_N\right]$}
			% XXX Algorithm
			\For(\tcp*[f]{At every time step})
            {$t = 1, \dots, T$}{
				%
				% \tcp{First, run each algorithm $\Alg_a$}
				\For(\tcp*[f]{Can be parallel}){$a = 1, \dots, N$}{
					$\Alg_a$ updates its internal state (e.g., \UCB{} indexes)\;
					It chooses $A_a(t+1) \in [K]$.
				}
				%
				% \tcp{The more algorithms have chosen arm $j$, the more probable it is to be chosen.}
				Let $p^{t+1}_j := \sum\limits_{a = 1}^{N} \pi^{t}_a \times \indic(\{A_a(t+1) = j\}), \;\forall 1\leq j \leq K$\;
				% \tcp*{Sum trusts}
				Then $\Alg_{\mathrm{aggr}}$ chooses arm $A(t+1) \sim p^{t+1}$\;
				% $\P(A(t+1)_{\mathrm{aggr}} = j) = p^{t+1}_j$
				% \tcp*{Sample once}
				%
				Give \emph{original} reward $(A(t+1), r(t+1))$ to \emph{each} $\Alg_a$ (maybe \emph{not} on its chosen arm)\;
				Compute an \emph{unbiased} estimate of the reward of the trusted algorithms,$$ \widehat{r}(t+1) = r(t+1) / p^{t+1}_{A(t+1)}\;. $$
				% \tcp{Use bandit feedback to update $\pi^{t}$}
				% \tcp{Finally, use the instantaneous bandit feedback (reward $\ell_{A(t+1),t}$) to update $\pi^{t}$}
				% \For(\tcp*[f]{Can be parallel}){$a = 1, \dots, N$}{
				\For{$a = 1, \dots, N$}{
					% \eIf{$\Alg_a$ was trusted, \ie, $A_a(t+1) = A(t+1)$}{
					\eIf{$\Alg_a$ was trusted, \ie, $A_a(t+1) = A(t+1)$}{
						$ \pi^{t+1}_{a} = \exp(\eta_t r(t+1) \times \pi^{t}_{a} $
						\tcp*{Trusted more}
						}{
						% $ \pi^{t+1}_{a} = \exp(- \eta_t r(t+1) \times \pi^{t}_{a} $
						$ \pi^{t+1}_{a} = \pi^{t}_{a} $
						\tcp*{Do not update the trust now}
					}
				}
				Renormalize the new weights $\pi^{t+1}$: $\pi^{t+1} := \pi^{t+1} / \sum_{a=1}^{N} \pi^{t+1}_{a}$.
				% \tcp*{Project it back to $\Delta_N$}
			}
			\caption{Our algorithm \Aggr{} aggregating $\Alg_1,\dots,\Alg_N$.}
			\label{algo:25:Aggr}
		\end{algorithm}
		\end{framed}
	\end{figure}
\end{small}

\TODOL{Etre sur des notations entre $t$ et $t+1$ pour faire comme le reste du chapitre et de la thèse !}

At every time step, after having observed a reward $r(t+1)=Y_{A(t+1),t+1}$ for its chosen action $A(t+1)$,
the algorithm updates the trust probabilities from $\pi^t$ to $\pi^{t+1}$ by
a multiplicative exponential factor (using the learning rate and the \emph{unbiased} reward).
%
Only the algorithms $\Alg_a$ who advised the last decision get their trust updated, in order to trust more the ``reliable'' algorithms.

The reward estimate is unbiased in the following sense. If one had access to the samples $Y_{k,t+1}$ for all arms $k$, the reward incurred by algorithm $a$ at time $t+1$ would be $r^a(t+1) = Y_{A_a(t+1),t+1}$.
But we are not in the full information setting (see \cite{CesaLugosi06}), but in the bandit setting, so only one of the samples $Y_{k,t+1}$ can be observed, $r(t)=Y_{A(t+1),t+1}$.
This quantity can only be observed for those algorithms $a$ for which $A_{a}^{t+1}=A(t+1)$.
However, by dividing by the probability of observing this recommendation, one obtains an unbiased estimate of $r^a(t+1)$. More precisely, if we define the estimate by
\begin{equation}
	\widehat{r^a}(t+1) = \frac{Y_{A_a(t+1),t+1}}{p_{A_a(t+1)}^{t+1}} \indic(A_a(t+1) = A(t+1))
\end{equation}
satisfies $\E_{\cO_t}[\widehat{r^a}(t+1) | \cO_t] = Y_{A_a(t+1),t+1}$, for all $a$, where the expectation is taken conditionally to the history of observations up to round $t$, $\cO_t$.
%
Observe that $\widehat{r^a}(t+1) = 0$ for all algorithms $a$ such that $A_a(t+1) \neq A(t+1)$.

% - Precise some tricky points
An important feature of \Aggr{} is the feedback provided to each underlying bandit algorithm, upon the observation of arm $A(t+1)$. Rather than updating only the trusted algorithms (that is the algorithms which would have drawn arm $A(t+1)$) with the observed reward $r(t+1)$, we found that updating each algorithm with the (original) reward observed for arm $A(t+1)$ improves the performance drastically.
%
As expected, the more feedback they get, the faster the underlying algorithms learn, and the better the aggregation algorithm is.
This intuition is backed up by theory explained in \cite{Maillard11}.

@@

% ----------------------------------------------------------------------
\textbf{Comparison with \ExpQ{}:}\label{sub:25:Exp4}
%
% - explain, but don't give pseudo-code ?
The \ExpQ{} algorithm dates from \cite{Auer02NonStochastic}, and for instance it is also well explained in Section~4.2 of \cite{Bubeck12}.
It is similar to \Aggr{}, presented in Algorithm~\ref{algo:25:Aggr},
but differs in the two following points.
%
The first difference is that $a\sim\pi^t$ is sampled first and the arm chosen by $\Alg_a$ is trusted, whereas \Aggr{}
needs to listen to the $N$ decisions to perform the updates on $\pi^{t+1}$.
Then, \ExpQ{} gives back an observation (arm, reward) only to the last trusted algorithm
whereas \Aggr{} gives it to all algorithms.
%
The second difference is that after having computed the reward estimate $\widehat{r^a}(t+1)$, \ExpQ{} updates the estimated cumulative reward for each algorithm,
$\widetilde{R}_a(t) = \sum_{s=1}^{t} \widehat{r^a}(t+1) \times \indic(A^{s}_{a} = A^{s}_{\mathrm{aggr}})$.
%
Instead
\footnote{~It is the same for constant learning rates, and does not differ much for decreasing learning rates.}
of updating $\pi^{t}$ multiplicatively as we do for our proposal, \ExpQ{} recomputes it, proportionally to
$\exp(\eta_t \widetilde{R}_a(t))$.
%
We also note that \ExpQ{} uses \emph{losses} instead of rewards, with $\ell(t) = 1 - r(t)$, but this is only a change of vocabulary.

@@

Figures~\ref{fig:25:EasyBernoulli} and~\ref{fig:25:HarderMixed} are in semilog-$y$ scale, this helps to see that the best algorithms can be an \emph{order of magnitude} more efficient than the worst, and the \Aggr{} performs similarly to the best ones, when the other aggregation algorithms are usually amongst the worst.
Figure~\ref{fig:25:HarderMixed_semilogx} is in semilog-$x$ scale to show that the regret of efficient algorithms are indeed logarithmic.

@@

For Bernoulli problems (Figures~\ref{fig:25:EasyBernoulli} and~\ref{fig:25:HardBernoulli}), UCB with $\alpha=1/2$, Thompson sampling, BayesUCB and \klUCB{}$^+$ (with the binary $\kl$ function) all perform similarly, and \Aggr{} is found to be as efficient as all of them.
For Gaussian and exponential arms, rewards are truncated into $[0,1]$, and the variance of Gaussian distributions is fixed to $\sigma^2 = 0.05$ for all arms, and can be known to the algorithms (the \kl{} function is adapted to this one-dimensional exponential family).
%
Figure~\ref{fig:25:EasyGaussian} uses only Gaussian arms, with a large gap between their means and a relatively small variance, giving an ``easy'' problem.
%
And Figure~\ref{fig:25:HarderMixed} shows a considerably harder ``mixed'' problem, when the distributions are no longer in the same one-dimensional exponential family and so the Lai \& Robbins' lower-bound no longer holds (even if there still exists a lower-bound).

For each of the 4 problems considered, the \Aggr{} algorithm with default option (\ie, broadcast rewards to all the aggregated algorithms) is the best of all the aggregation algorithms,
and its regret is very close to the best of the aggregated algorithms.
Especially in difficult problems with mixed or unknown distributions, \Aggr{} showed to be more efficient that \ExpQ{} and orders of magnitude better than the other reference aggregation algorithms \LearnExp{} and \CORRAL{} (see Figures~\ref{fig:25:HarderMixed} and~\ref{fig:25:HarderMixed_semilogx}).
